\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Design Guideline}
\author{Authors: }
\date{Somethingary 2025}

\begin{document}

\maketitle

\newpage
\section{Consept phase}
In the concept phase, before writing code, you should decide the general rules and direction:
\begin{enumerate}
    \item Theme: how serious or playful the design should be
    \item Color scheme:
    \begin{itemize}
        \item Does the company have a color scheme?
        \item Which colors are suggested by the theme of the site?
        \item Pick the main color
        \item Pick an accent color (optional)
    \end{itemize}
    \item Hierarchy and layout:
    \begin{itemize}
        \item What is the most important message/product on the page?
        \item What is the order of importance for the different elements?
        \item What sections will there be on the page?
        \item What layout(s) will you use for the sections?
    \end{itemize}
    \item Images:
    \begin{itemize}
        \item Gather the available images
        \item Will there be text on images or aside images?
        \item Will we use clear images or a color-overlay?
        \item Will there be blur for images?
    \end{itemize}
    \item Icons:
    \begin{itemize}
        \item Will we use icons and for what?
        \item Colored or black-and-white/greyscale icons?
    \end{itemize}
    \item Typography:
    \begin{itemize}
        \item Should it by a Serif or Sans-Serif font?
        \item Bold or thin font?
        \item Rounded or sharp edges?
    \end{itemize}
    \item Border rounding:
    \begin{itemize}
        \item How rounded should be the edges, according to the theme?
    \end{itemize}
        \item Shadows:
    \begin{itemize}
        \item How much shadow will we use in general, according to the theme?
    \end{itemize}
\end{enumerate}


\newpage
\section{Sketching}
Create a sketch of the page which shows the general layout of the page.

\noindent\hrulefill

\section{Specific Technical Decisions }
This comes at a later stage when you start implementing the site:
\begin{enumerate}
    \item Colours:
    \begin{itemize}
        \item Generate color shades/tints (See video 2.2.3 Colors)
    \end{itemize}
    \item Typography:
    \begin{enumerate}
        \item[a] Choose a font for titles (You will probably want to change it when you see the site, but
start with something)
        \item[b] If body text needs another font, choose it. Preferably, use the same font for all texts.
        \item[c] Define font scale using https://type-scale.com/
    \end{enumerate}
    \item Hierarchy and layout:
    \begin{enumerate}
        \item[a] Which elements will need an accent because we want to increase their priority in the
hierarchy?
        \item[b] What components will we need to implement the necessary layouts?
    \end{enumerate}
    \item Icons:
    \begin{enumerate}
        \item[a] Choose icon pack if you need one. See http://codingheroes.io/resources/icons
    \end{enumerate}
    \item  Spacing:
        \begin{enumerate}
        \item[a] Define spacing scale, f.ex, multiples of 16px (multiples of 4px for smaller padding)
    \end{enumerate}
    \item  Border rounding:
        \begin{enumerate}
        \item[a] Synchronize the chosen font with roundedness (very rounded font → more border
rounding for elements)
        \item[b]  Border rounding amount for general elements: cards, forms, images, etc
        \item[c] Border rounding for buttons
    \end{enumerate}
\end{enumerate}

\end{document}