
\documentclass{article}
\begin{document}
\section{Rental Roulette Ideas}


\section{Product Functionality}

- You first choose the cities you want to pick up and drop off the car, along with the dates.
- Then, all the cars available for those dates and cities are displayed.

\subsection{Features:}

When a person places an order for a car on a specific date and city, this information is communicated to the back-end. The availability of that car is updated, ensuring no one else can rent it.

\subsection{Filters:}
\begin{itemize}
    \item Price (range)
    \item Passengers
    \item Acceleration
    \item Top speed
    \item Sedan, SUV, cabriolet, familiebil, stasjonsvogn, elektrisk, luksus/sport
    \item Fuel Type
    \item Manual vs automatic
    \item Brand/car maker – Tesla vs Volkswagen
    \item Driver's age: the older, the cheaper it is (insurance).
    \item Model - 2008 vs. 2020
    \item Extra features: Bluetooth, DAB radio, heated seats
\end{itemize}

\subsection{Mandatory Requirements – Common}
A complete website must be implemented. Both the frontend and backend must support the entire process of product filtering:
\begin{itemize}
    \item Landing page
    \item Product search (search form and search result list/grid)
    \item Choosing one specific product
    \item Product detail page (for the chosen product):
    \begin{itemize}
        \item Product image
        \item Product description
        \item Product price for the different providers
    \end{itemize}
    \item Placing an order (this action may vary depending on the project theme; propose a solution and present it to the customer (teachers)).
    \item Login form
    \item For logged in users:
    \begin{itemize}
        \item Regular users:
        \begin{itemize}
            \item Can add a product to their favorite list.
            \item Can see their favorite products.
        \end{itemize}
        \item Admin users:
        \begin{itemize}
            \item Can show and hide a product. A hidden product does not appear to regular users.
        \end{itemize}
    \end{itemize}
\end{itemize}

\section{Design Ideas}

\subsection{Login Page}
\begin{itemize}
    \item When selecting an element, the bar under the text glows orange. Normally the bar is gray
    \item When you hover over forgot password/register, the text glows orange and the field's text moves up.
    \item If you try to log in without filling the elements, the bar becomes red, and red text below the bar explaining the problem appears.

\subsection{Booking page}
\item When you book a car, you have a picture on the left with the car, and you can do a photo carousel to look at the different photos.
\end{itemize}
\end{document}