
\documentclass{article}
\begin{document}


\textbf{Sprint 1 - 28.01.25–08.02.25} 
\textbf{Sprint Goal} 

\begin{itemize}
    \item Project startup
    \begin{itemize}
        \item Create wireframe
        \begin{itemize}
            \item Home site
            \item Booking sites
            \item Login site
        \end{itemize}
        \item Create Doc-page
        \begin{itemize}
            \item Describe main demographic
            \item Create product specifications
            \item List functionalities for MVP
        \end{itemize}
        \item Initialize project
        \begin{itemize}
            \item Set up repositories
            \item Create a base file structure
        \end{itemize}
        \item Establish sprint board and collaboration routines
        \begin{itemize}
            \item Create sprint board
            \item Establish rules for code reviews and pull requests
        \end{itemize}
    \end{itemize}
\end{itemize}

\textbf{Sprint Backlog} 

\textbf{Time Frame} 

28.01.25–08.02.25 

\textbf{Roles and Responsibilities} 

\begin{itemize}
    \item Marcus → Wireframes
    \item Mathias → Create Doc-page
    \item Petter → Initialize project, establish sprint board
\end{itemize}

\textbf{Expected Results} 

\begin{enumerate}
    \item Fully Initialized Project
    \begin{itemize}
        \item The development environment is established and works as intended.
        \item Repositories are configured and available for the rest of the team.
        \item Base file structure is established, and the team understands the file organization.
    \end{itemize}
    \item Wireframes ready for review
    \begin{itemize}
        \item Finished wireframes for the homepage, booking pages, and login page.
    \end{itemize}
    \item Comprehensive Documentation
    \begin{itemize}
        \item An updated doc-page contains: 
        \begin{itemize}
            \item Description of main demographic
            \item Product specification with focus on MVP
            \item A list of core functionalities to be implemented
            \item A visualized or described process flow from user interaction to booking
        \end{itemize}
    \end{itemize}
    \item Sprint Workflow established
    \begin{itemize}
        \item Sprint board is established with tasks assigned to team members.
        \item Clear rules for cooperation (Definition of Done, rules for code reviews and pull requests).
        \item Team has a defined workflow to use throughout the project.
    \end{itemize}
\end{enumerate}

\textbf{Risks and Challenges} 

\paragraph{1. Project Initialization}
\begin{itemize}
    \item \textbf{Risk:} Team members may face issues setting up the development environment (e.g., dependency conflicts, configuration errors).
    \item \textbf{Challenge:} Ensuring all members have a consistent setup across different machines.
    \item \textbf{Mitigation:} Provide detailed setup instructions and use a \verb|.env| file or Docker for uniform environments.
\end{itemize}

\paragraph{2. Wireframe Creation}
\begin{itemize}
    \item \textbf{Risk:} Misalignment between the wireframes and stakeholders' expectations.
    \item \textbf{Challenge:} Ensuring the wireframes are detailed enough to guide development but flexible enough for future changes.
    \item \textbf{Mitigation:} Schedule a mid-sprint review session for early feedback on wireframes.
\end{itemize}

\paragraph{3. Documentation}
\begin{itemize}
    \item \textbf{Risk:} Unclear or incomplete documentation, such as missing details on the demographic or MVP functionality.
    \item \textbf{Challenge:} Balancing documentation detail with sprint timelines.
    \item \textbf{Mitigation:} Assign a dedicated team member to oversee documentation quality and completeness.
\end{itemize}

\paragraph{4. Collaboration and Teamwork}
\begin{itemize}
    \item \textbf{Risk:} Miscommunication about task ownership or scope.
    \item \textbf{Challenge:} Team members might not fully understand the "Definition of Done" or the code review process.
    \item \textbf{Mitigation:} Conduct a kickoff meeting to clarify roles, expectations, and collaboration routines.
\end{itemize}

\paragraph{5. Time Management}
\begin{itemize}
    \item \textbf{Risk:} Overestimating the amount of work the team can complete within the sprint.
    \item \textbf{Challenge:} Prioritizing tasks effectively and avoiding burnout or scope creep.
    \item \textbf{Mitigation:} Focus on completing MVP-level tasks first and leave stretch goals as optional.
\end{itemize}

\paragraph{6. Sprint Board and Workflow Setup}
\begin{itemize}
    \item \textbf{Risk:} Poorly defined sprint board tasks may lead to ambiguity and delays.
    \item \textbf{Challenge:} Ensuring tasks are granular enough to be actionable but not overly detailed.
    \item \textbf{Mitigation:} Use templates for task creation and involve the team in breaking down larger tasks.
\end{itemize}

\paragraph{7. Team Alignment and Availability}
\begin{itemize}
    \item \textbf{Risk:} Team members may have differing levels of experience or availability.
    \item \textbf{Challenge:} Ensuring everyone stays productive and aligned.
    \item \textbf{Mitigation:} Schedule daily stand-ups to track progress and resolve blockers early.
\end{itemize}

\end{document}